Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-25 paper/paper.tex
pass

\vspace{2ex}
\noindent\textbf{Limitations.} It is worth noting that although
\tname{} is accurate for generating rules that discrimate positive and
negative traffic, the quality of these rules is limited by the quality
of the training data it uses. For the positive traffic, \tname{} only
requires one sample, but can benefit of several samples as the example
from Section~\ref{sec:dos} illustrated. The same applies for the
negative traffic. In this case, however, \tname{} can use public
data sets available online.

\vspace{2ex}
\noindent\textbf{Implementation details.} We implemented function
\emph{isPlausible} by 1)~updating Suricata to only use the rule that
is passed as parameter to this function, 2)~replaying the negative
traffic (see Section~\ref{sec:dataset-benign}), and 3)~reading the
Suricata logs to check if any benign message was captured by the
rule. It is worth noting that the benign traffic is stored in ``pcap''
files~\cite{pcap} and Suricata can process those files very
efficiently compared to analyzing network messages directly.

@@

\textbf{Rationale.}~The golden rule is a rule that is known to capture
a given attack. \tname\ generates several rules that satisfy the
invariant to only capture the malicious traffic, but the amount of
data we use to assess that invariant, albeit large, is limited. In
fact, assessing quality of each rule (\ie{}, fitness to the attack)
requires domain knowledge. The position of the golden rule at the
ranking produced by \tname\ is a proxy measure to the effort of a
system administrator in finding the rule that fits the purpose.

@@

    %%Black Nurse \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:3; icode:3; detection\_filter:track by\_dst, count 250, seconds 1;}\\
    %%Ping Flood  \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:8; icode:0; detection\_filter:track by\_src, count 30, seconds 1;}\\  
    %%Port Scan \MyComment{& single} & TCP \MyComment{& Discovers open ports in a host} & \scriptsize{flags: A; ack: 0;dsize: 0;} \\

    %%UDP Flood \MyComment{& multiple} & UDP \MyComment{& Denial of Service} & \scriptsize{fragbits:M; threshold: type both, track by\_dst, count 5000, seconds 5;} \\

@@

\subsection{Methodology}

Recall that Suricata is invoked multiple times in the process of
minimizing the rule (see Section~\ref{sec:minimization}). Suricata
supports a feature to process ``pcap'' files, enabling very efficient
performance compared to processing actual network messages.

@@

\subsection{Answering RQ1: \textRQone}

\subsection{Answering RQ2: \textRQtwo}

@@

\subsection{Threats to Validity}

>>>>

\textbf{Implementation details.} We implemented function
\emph{isPlausible} by 1)~updating Suricata to only monitor the rule
that is passed as parameter, 2)~replaying the negative traffic (see
Section~\ref{sec:dataset-benign}), and 3)~reading the Suricata logs to
check if any benign message was captured by the rule. It is worth
noting that the benign traffic is stored in ``pcap'' files~\cite{pcap}
and Suricata can process those files very efficiently compared to
analyzing network messages directly. Instead of sending traffic to a
machine with a deployed server (\eg{}, web server) that
\suri\ monitors, our setup calls Suricata directly through an
API. Suricata is invoked multiple times in the process of minimizing
the rule.
\textbf{Limitations.} It is worth noting that although
\tname{} is accurate for generating rules that discrimate positive and
negative traffic, the quality of these rules is limited by the quality
of the training data it uses. For the positive traffic, \tname{} only
requires one sample, but can benefit of several samples. The same
applies for the negative traffic. In this case, however, \tname{} can
use public data sets available online.

@@

\noindent
\textbf{Rationale.}~The golden rule is a trusted human-written rule
obtained from credible sources. \tname\ generates several rules that
satisfy the invariant to only capture the malicious traffic, but the
amount of data we use to evaluate that property, albeit large, is
limited. Assessing the quality of each rule \tname\ produces (\ie{},
fitness to the attack) requires domain knowledge and much effort. The
position of the golden rule at the ranking produced by \tname\ is a
proxy measure to the effort a system administrator would have in
finding the rule that fits the purpose.

@@

\noindent
\textbf{Rationale.}~\tname\ proposes a variety of heuristic functions
to rank the plausible rules produced during minimization. It is
therefore important to understand how much each function contributes
to the overall performance of the technique.

\newcommand{\textRQthree}{What is the importance of the positive and
  negative traffic in ranking?}
\vspace{0.2cm}
\begin{itemize}[leftmargin=*]
\item{\textbf{RQ3.}} \textRQthree\
\end{itemize}

\noindent
\textbf{Rationale.}~\tname\ uses both positive and negative examples
to generate rules. This question investigates how sensible the
technique is to the traffic that it uses.
\noindent
\vspace{1ex}

The following sections describe the objects we used to evaluate the
technique (Section~\ref{sec:dataset-benign}), answer the questions
(sections~\ref{sec:answer-rqone},~\ref{sec:answer-rqothree}), and
discuss threats to the validity of the
experiments~(Section~\ref{sec:threats}).

@@

%subsection{Methodology}

@@

\subsection{Answering RQ1: \textRQone}
\label{sec:answer-rqone}

\subsection{Answering RQ2: \textRQtwo}
\label{sec:answer-rqotwo}

\subsection{Answering RQ3: \textRQthree}
\label{sec:answer-rqothree}

@@

\subsection{Threats to Validity}
\label{sec:threats}
